---
title: "PDA"
author: "Rohith Srinivas"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
# Add code here to load all the required libraries with `library()`.  
# Do not include any `install.package()` for any required packages in this rmd file.

library(tidyverse) # Streamline data manipulation and visualization with a cohesive set of tools.
library(ggplot2)   # Create customizable plots and charts with the Grammar of Graphics.
library(plotly)    # Load the 'plotly' library for creating interactive plots.
library(validate)  # Perform data validation and quality checks for enhanced data integrity.
library(Hmisc)     # Access advanced data manipulation, imputation and statistical functions for in-depth analysis.
library(modeest)   # To use mode/mfv
library(gridExtra) # To use grid arrange
library(car)       # To use vif()
```

# 1. Organise and clean the data

## 1.1 Import Dataset

```{r}
movies_df <- read.csv("movies.csv",na.strings=c("","NA"))
```

## 1.2 Data quality analysis plan

```{r}
# Generate summary statistics for the 'mydf' data frame.
summary(movies_df)
```

The dataset has 17 variables (columns) and 2100 observations (rows).

## 1.3 Data quality analysis findings

### Renaming Columns

```{r}
movies_df <- movies_df %>% 
  rename(
     Content_Rating =  Content.Rating,
     Aspect_Ratio  = Aspect.Ratio,
     Gross_Earnings = Gross.Earnings,
     Reviews_by_Users = Reviews.by.Users,
     Reviews_by_Critics = Reviews.by.Crtiics,
     IMDB_Score = IMDB.Score 
    )
```

### Unique Rows

```{r}
# Check for any duplicated rows
duplicate_rows <- movies_df[duplicated(movies_df), ]
movies_df <- movies_df[!duplicated(movies_df), ]
```

### Completeness

```{r}
# Calculate the count of missing values in each column of 'mydf' and store the results in 'na_table'.
na_table <- colSums(is.na(movies_df))
na_table
```

```{r}
movies_df_imputed <- movies_df %>%
  # Impute Language based on the mode 
  mutate(
    Language = if_else(is.na(Language), as.character(mfv(Language)), Language),

  # Impute Duration with the mean of Duration
  Duration = if_else(is.na(Duration), mean(Duration, na.rm = TRUE), Duration),
  
  # Impute Aspect Ratio with the mode of Aspect Ratio
  Aspect_Ratio = if_else(is.na(Aspect_Ratio), mfv(Aspect_Ratio), Aspect_Ratio),
  
  # Impute Budget and Gross Earnings with their median values
  Budget = if_else(is.na(Budget), median(Budget, na.rm = TRUE), Budget),
  Reviews_by_Users = if_else(is.na(Reviews_by_Users), median(Reviews_by_Users, na.rm = TRUE), Reviews_by_Users),
  Reviews_by_Critics = if_else(is.na(Reviews_by_Critics), median(Reviews_by_Critics, na.rm = TRUE), Reviews_by_Critics),
  
  Gross_Earnings = if_else(is.na(Gross_Earnings),  median(Gross_Earnings, na.rm = TRUE), Gross_Earnings)
  )
```

```{r}
x <- movies_df_imputed[is.na(movies_df_imputed$Actor1) & is.na(movies_df_imputed$Actor2) & is.na(movies_df_imputed$Actor3),]
#Removing these would be better
movies_df_imputed <- movies_df_imputed[!is.na(movies_df_imputed$Actor1) | !is.na(movies_df_imputed$Actor2) | !is.na(movies_df_imputed$Actor3),]

na_table <- colSums(is.na(movies_df_imputed))
na_table
movies_df <- movies_df_imputed
```

### Consistency

```{r}
valid_languages <- c("English","Spanish","German","Mandarin","Hindi","Japanese","Persian","French","Norwegian","Cantonese","Thai","Portuguese","Russian","Aboriginal","Korean","Dari","Italian","Dzongkha","Swedish","Aramaic","Hungarian","Kazakh","Filipino","Zulu","Maya","Dutch","Czech","Vietnamese","Hebrew","Arabic","Romanian","Mongolian","Danish","Greek")
valid_countries <- c("USA","UK","Mexico","Germany","France","Taiwan","Denmark","India","Argentina","Japan","Australia","Iran","Norway","Canada","Hong Kong","Thailand","New Zealand","New Line","Brazil","China","Sweden","Spain","Italy","South Korea","Afghanistan","Russia","Ireland","Colombia","Romania","Philippines","Hungary","Cameroon","Netherlands","South Africa","Czech Republic","Israel","Poland","Turkey","Slovakia","Switzerland","Greece","Iceland")
valid_aspect_ratios <- c("1.85","1.37","2.35","1.44","1.66","1.78","1.33","1.5","2","2.4","2.39","1.75","2.55","16")
```

```{r}
# Define validation rules for the movies dataset
movies.rules <- validator(
  OKyear = Year >= 2000 & Year <= 2010,  # Assuming movies can't be before 1900 or in the future
  OKduration = Duration > 0,  # Duration should be positive
  OKaspectratio = Aspect_Ratio >= 1.33 & Aspect_Ratio <= 2.40,  # Common aspect ratios
  OKbudget = Budget > 0,  # Budget should be positive
  OKgross = Gross_Earnings >= 0,  # Gross earnings can be zero but not negative
  OKimdb = IMDB_Score > 0 & IMDB_Score <= 10,  # Valid IMDB score range
  OKreviewsusers = Reviews_by_Users >= 0,  # Number of user reviews can be zero but not negative
  OKreviewscritics = Reviews_by_Critiics >= 0,  # Number of critic reviews can be zero but not negative
  OKcontentrating = is.element(Content_Rating, c("G", "PG", "PG-13", "R", "NC-17", "Not Rated", "Unrated"))  # Valid content ratings
)

# Assuming your dataframe is named movies_df
# Perform quality checks on 'movies_df' data frame using the 'movies.rules' validation rules
movies_qual_check <- confront(movies_df, movies.rules)

# Summarize the quality check results
summary(movies_qual_check)

# Create a quality check plot.
plot(movies_qual_check, xlab=" ")
```

### Integrity

```{r}
# structure of the 'movies_df' data frame
str(movies_df)
```


```{r}
# Create binary indicators for each genre
GenreList <- strsplit(as.character(movies_df$Genres), " ")
unique_genres <- unique(unlist(GenreList))

for(genre in unique_genres) {
  movies_df[genre] <- sapply(GenreList, function(g) as.integer(genre %in% g))
}

if(`Sci-Fi` %in% names(movies_df))
{
  movies_df <- movies_df %>%
  rename(
    Sci_Fi = `Sci-Fi`
    )
}


# # Now, to filter movies that are in Comedy including those that are also Action and Drama
#  comedy_movies <- movies_df[sapply(movies_df$GenreList, function(x) "Comedy" %in% x & "Horror" %in% x), ]
# 
# unique_genre <- sort(unique(unlist(movies_df$GenreList)))
# onehot <- function(x) {
#   temp <-""
#   for (g in unique_genre)
#   {
#     temp <- paste(temp,as.character(ifelse(g %in% x,'1','0')),sep = '')
#   }
#   print(temp)
# }
# # movies_df[sapply(movies_df$GenreList,onehot(x)),]
# onehot(c("Comedy", "Horror", "Mystery"))
```


```{r}
# Convert the categorical variables in 'movies_df' to factors for categorical representation.
movies_df <- movies_df %>%
  mutate(
    Content_Rating = as.factor(Content_Rating),
    Language = as.factor(Language),
    Country = as.factor(Country),
    Aspect_Ratio = as.factor(Aspect_Ratio),
    Adventure = as.factor(Adventure),
    Comedy = as.factor(Comedy),
    Family = as.factor(Family),
    Drama = as.factor(Drama),
    Romance = as.factor(Romance),
    Western = as.factor(Western),
    Music = as.factor(Music),
    Crime = as.factor(Crime),
    Thriller = as.factor(Thriller),
    Horror = as.factor(Horror),
    Action = as.factor(Action),
    Sci_Fi = as.factor(Sci_Fi),
    Fantasy = as.factor(Fantasy),
    Mystery = as.factor(Mystery),
    Sport = as.factor(Sport),
    Animation = as.factor(Animation),
    Musical = as.factor(Musical),
    Biography = as.factor(Biography),
    Documentary = as.factor(Documentary),
    History = as.factor(History),
    War = as.factor(War),
    Short = as.factor(Short),
    News = as.factor(News)
  )

# Re-evaluating the structure of the 'movies_df' data frame
str(movies_df)
```

### Accuracy

```{r}
# Check for outliers
sapply(movies_df[,sapply(movies_df, is.numeric)], function(x) boxplot(x, plot = FALSE)$out)
```

```{r}
write_csv(movies_df,file = "movies_imputed.csv")
```

1.  **Column Names**: Some column names contain periods (`.`) and are not consistent (e.g., `Content.Rating` instead of `Content_Rating`). The columns `Content_Rating`, `Aspect_Ratio`, `Gross_Earnings`, `Reviews_by_Users`, `Reviews_by_Crtiics`, `IMDB_Score` were standardized.
2.  **Duplicate Rows**: There were 42 duplicate rows identified and subsequently removed from the dataset.
3.  **Missing Values**: There are missing values in several columns (e.g., `Content.Rating` and `Duration`). We'll need to decide on a strategy for handling these, such as filling them in with default values or removing rows/columns with too many missing values.
4.  **Data Types**: Most columns have the correct data type. Categorical data such as content rating, aspect ratio, language, country as well as the newly created genre columns are converted as factor.
5.  **Outliers and Anomalies**: We'll need to check for outliers or anomalies in numerical columns (e.g., `Budget`, `Gross.Earnings`, `Duration`).
6.  **Consistency in Categorical Data**: For columns like `Language`, `Country`, and `Genres`, we should ensure consistency in naming and consider grouping rare categories under a single label if necessary.

```{r}
# Assuming that movies_df is your cleaned dataset and it's already been loaded into your R environment
library(cluster)

# Select only numerical columns for clustering
numerical_data <- movies_df_imputed %>% select_if(is.numeric)

# Standardize the data
numerical_data_scaled <- scale(numerical_data)

# Perform K-means clustering
# set.seed(123) # Set seed for reproducibility
kmeans_result <- kmeans(numerical_data, 3)  # Assuming we want to create 3 clusters

kmeans_result $cluster

# Attach cluster results to the original data
movies_df_imputed$cluster <- kmeans_result$cluster

# Visualize clusters with a plot, we'll need to reduce dimensions to do so.
# We can use PCA for this.
pca_for_plot <- prcomp(numerical_data_scaled)
plot(pca_for_plot$x[,1:2], col = kmeans_result$cluster, pch = 20, xlab = "PC1", ylab = "PC2")

```

