---
title: "DecisionTree"
author: "leonardo_2368386"
date: "2024-03-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Decision Tree ML method

## Load libraries
```{r}
# install the rpart package (if needed) to create the decision tree model
if(require(rpart) == FALSE){
  install.packages('rpart')
  library(rpart)
}
# install the tidymodels package (if needed), to evaluate the model's performance
if(require(tidyverse) == FALSE){
  install.packages("tidyverse")
  library(tidyverse)
}

```

## 1.Load datasets

```{r}

movies_dataset <- read.csv("movies_final.csv", stringsAsFactors = T)

#70/30 split
training_movies <- read.csv("training_movies.csv", stringsAsFactors = T)

testing_movies <- read.csv("testing_movies.csv", stringsAsFactors = T)

```

## 2.Data preparation

```{r}

# Removal of the title column
training_movies <- training_movies[,-1]
testing_movies <- testing_movies[,-1]

summary(movies_dataset)
str(movies_dataset)

summary(training_movies)
str(training_movies)

summary(testing_movies)
str(testing_movies)

print("number of rows in the training set")
nrow(training_movies)

print("number of rows in the testing set")
nrow(testing_movies)

```

## 3.Decision tree model training

```{r}

# Create decision tree model using regression 
#input variables:
# -Duration
# -Budget
# -Reviews_by_Users
# -IMDB_Score
#output variables:
# -Gross_Earnings
  
DT_model <- rpart(Gross_Earnings ~ Duration + 
             Budget + Reviews_by_Users + IMDB_Score,  
             method = "anova", data = training_movies)

```

## 4.Model view (Plots)

```{r}

plot(DT_model, uniform = TRUE, 
          main = "Gross_Earnings Decision  
                 Tree using Regression") 
text(DT_model, use.n = TRUE, cex = .7)

print(DT_model)

```

## 5.Decision Tree prediction

```{r}

#prediction of the testing set values
cat("Predicted value:\n") 
DT_pred <- predict(DT_model, testing_movies, method = "anova") 

```

## 5.Decision Tree performance evaluation

```{r}

#To evaluate the model's performance we are going to use metrics such as root mean squared error (RMSE) and the R-squared value

# Calculate RMSE and R-squared

# Testing set true "Gross_Earnings" values
actual_DT_values <- testing_movies$Gross_Earnings

#plot actual values vs predicted values
plot(actual_DT_values, DT_pred, 
     xlab = "Actual Values", 
     ylab = "Predicted Values", 
     main = "Actual vs. Predicted Values")

abline(0, 1, col = "red")

legend("topleft", legend = "Ideal Fit", col = "red", lty = 1, cex = 0.8)

# Calculate RMSE
RMSE_value <- rmse(DT_pred, actual_DT_values)

# calculate r-squared
rsq <- function(x, y) summary(lm(y~x))$r.squared
r2 <- rsq(DT_pred, actual_DT_values)

# Print the metrics
cat("RMSE:", RMSE_value, "\n")
cat("R2:", r2, "\n")

```

  By looking at the results, we can say that the r-squared value obtained shows that approximately 53.15% of the variance in the dependent variable "Gross_Earnings" can be explained by the other independent variables used in the model, which means we got considerably good results with this metric. 
  On the other hand, the root mean squared error (RMSE) obtained by this model shows a poor performance, as the value is quite high. This can be explained by the weak relationship existent between the variables used in this model, such as the lack of linear relations.

#based on the following sources:
-https://www.datacamp.com/tutorial/decision-trees-R
-https://www.geeksforgeeks.org/decision-tree-for-regression-in-r-programming/
