---
title: "CS5812-Dua-NN"
output: html_document
date: "2024-03-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# install and load the neuralnet package from CRAN
if(require(neuralnet) == FALSE){
  install.packages('neuralnet')
}
```

#### 2. Data preparation
```{r}

# read the data from the movies.csv file
movies <- read.csv("movies_final.csv")

# inspect the data
str(movies)
movies_df<-subset(movies, select = -Title)
set.seed(48)
# transform the data using a min-max function
MinMax <- function(x){
  tx <- (x - min(x)) / (max(x) - min(x))
  return(tx)
}
movies_minmax <- apply(movies_df, 2, MinMax)

movies_minmax <- as.data.frame(movies_minmax)

# create a 70/30 training/test set split
n_rows <- nrow(movies_minmax)
# sample 70% (n_rows * 0.7) indices in the ranges 1:nrows
training_idx <- sample(n_rows, n_rows * 0.7)
# filter the data frame with the training indices (and the complement)
training_movies_minmax <- movies_minmax[training_idx,]
test_movies_minmax <- movies_minmax[-training_idx,]
```

#### 3. Neural network training{#Neural_network_training}
```{r}
# define a formula for predicting gross_earnings
grossearning_formula = Gross_Earnings ~ Duration+Budget+Reviews_by_Users+IMDB_Score

# train a neural network with 1 hidden node
gs_nn_1 <- neuralnet(grossearning_formula , data = training_movies_minmax)

# train a neural network with 4 nodes on one hidden layer
gs_nn_4 <- neuralnet(grossearning_formula , hidden = 4, data = training_movies_minmax)

# train a neural network with 4 nodes on each of two hidden layers
gs_nn_44 <- neuralnet(grossearning_formula , hidden = c(4,4), data = training_movies_minmax)

# plot the three neural networks and compare their structure
plot(gs_nn_1)
plot(gs_nn_4)
plot(gs_nn_44)
```

#### 4. Neural network prediction{#Neural_network_prediction}
```{r}
# compute the prediction for each neural network
pred_gs_nn_1 <- compute(gs_nn_1, test_movies_minmax[,-5])
pred_gs_nn_4 <- compute(gs_nn_4, test_movies_minmax[,-5])
pred_gs_nn_44 <- compute(gs_nn_44, test_movies_minmax[,-5])

# create a table with actual values and the three predictions
gs_results <- data.frame(
  actual = test_movies_minmax$Gross_Earnings,
  nn_1 = pred_gs_nn_1$net.result,
  nn_4 = pred_gs_nn_4$net.result,
  nn_44 = pred_gs_nn_44$net.result
)

# calculate the correlation between actual and predicted values to identify the best predictor
cor(gs_results[,'actual'], gs_results[,c("nn_1","nn_4", "nn_44")])

# plot actual vs predicted values for the worst (blue) and best predictor (orange)
#   note: points is used to add points on a graph
plot(
  gs_results$actual,
  gs_results$nn_1,
  col = 'blue',
  xlab = 'actual result',
  ylab = 'predicted result',
  xlim = c(0,1),
  ylim = c(0,1)
)
points(
  gs_results$actual,
  gs_results$nn_4,
  col = 'orange'
)
abline(a = 0, b = 1, col = 'red', lty = 'dashed')
legend(
  'topleft',
  c('nn_1', 'nn_4'),
  pch = 1,
  col = c('blue', 'orange'),
  bty = 'n'
)
```

I trained three neural networks with different hyper-parameters. As I had 4 independent variables, I choose four neuron per hidden layer in order to train my model. The results obtained by the performance evaluation of each trained model are as follows:
1. One Hidden node- 79%
2. One hidden layer with 4 nodes- 82%
3. Two hidden layers with 4 nodes each- 80%

Hence, we can conclude the neural network with one hidden layer was the best among the three for predicting gross earning with accuracy 82%. 

