---
title: "EDA (Content rating, duration, aspect ratio)"
output: html_document
date: "2024-02-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(ggmosaic)
library(dplyr)
Movies <- read.csv("movies_clean.csv")
View(Movies)
```

# Summary:

All my independent variables (Content rating, duration, aspect ratio) were all statistically significant with regard to both dependent variables (IMDB score and Gross earnings), HOWEVER all their p\^2 values were very small.

## Content rating vs target variable(s)

First the content rating and the target variable is compared, to determine whether a relationship/correlation exists between them. If there is no correlation/relationship between them, then it is to be excluded (in the cleaned data set), and therefore it is meaningless to compare the content rating with other independent variables. However, I have done it just in case...

NOTE: We haven't yet decided which variable will be our target variable: IMDB score or Gross earnings, so both variables have been analysed

```{r}
# Content rating vs IMDB score
ggplot(Movies, aes(x = Movies$Content_Rating, y = Movies$IMDB_Score)) +
  geom_boxplot() +
  theme_classic()
# Result: Median (and IQR) IMDB score of different content rating types are similar # except TV-G
```

```{r}
# Content rating vs Gross earnings
## Calculate mean gross earnings by content rating
mean_ge <- Movies %>% 
  group_by(Content_Rating) %>%
  summarise(mean_ge = mean(Gross_Earnings, na.rm = TRUE))
## Plot
ggplot(mean_ge, aes(x = Content_Rating, y = mean_ge)) +
  geom_bar(stat = "identity", fill = "black", color = "black") +
  geom_text(aes(label = sprintf("%.1e", mean_ge)),
            position = position_stack(vjust = 0.5), color = "red") +
  labs(title = "Content rating vs Mean Gross earnings",
       x = "Content Rating",
       y = "Mean Gross earnings") +
  theme_classic()
# Result: Big difference in mean budget between G, PG, PG-13, R & NC-17, Not rated # TV-G, Unrated, NA.

## Boxplot
ggplot(Movies, aes(x = Movies$Content_Rating, y = Movies$Gross_Earnings)) +
  geom_boxplot() +
  theme_classic()

summary(aov(Movies$Gross_Earnings~Movies$Content_Rating,data=Movies))

# Calculate the R - squared value
CRvGE_model <- summary(lm(Movies$IMDB_Score ~ Movies$Content_Rating, data = Movies))
# Get the summary of the model, which includes R-squared
CRvGE_model_R2 <- CRvGE_model$r.squared
print(CRvGE_model_R2)
# Result: Extremely low R^2 value (1.94%)
```

## Content rating vs. other independent variables

```{r}
# Content rating vs Year
Movies$Year <- factor(Movies$Year)
ggplot(Movies, aes(x = Content_Rating, fill = Year)) +
  geom_bar(position = "fill") +
  labs(title = "Content rating vs Year",
       x = "Content rating",
       y = "Proportion",
       fill = "Year")
# Result: Both NC-17 & TV-G were produced only for 2 different years, whilst others # were produced for more than 5 different years

# Content rating vs Language
ggplot(Movies, aes(x = Content_Rating, fill = Language)) +
  geom_bar(position = "fill") +
  labs(title = "Content rating vs Language",
       x = "Content rating",
       y = "Proportion",
       fill = "Language")
# Result: All content rating types were mostly English languaged based

# Content rating vs Country
ggplot(Movies, aes(x = Content_Rating, fill = Country)) +
  geom_bar(position = "fill") +
  labs(title = "Content rating vs Country",
       x = "Content rating",
       y = "Proportion",
       fill = "Country")
# Result: Most of the content rating types were mostly produced in the USA.

# Content rating vs Duration
## Calculate mean duration by content rating
mean_duration <- Movies %>% 
  group_by(Content_Rating) %>%
  summarise(mean_duration = mean(Duration, na.rm = TRUE))
## Plot
ggplot(mean_duration, aes(x = Content_Rating, y = mean_duration)) +
  geom_bar(stat = "identity", fill = "black", color = "black") +
  geom_text(aes(label = round(mean_duration, 0)),
            position = position_stack(vjust = 0.5), color = "red") +
  labs(title = "Content rating vs Mean Duration",
       x = "Content Rating",
       y = "Mean Duration") +
  theme_classic()
# Result: Nothing meaningful to decipher

# Content rating vs Aspect ratio
Movies$Aspect_Ratio <- factor(Movies$Aspect_Ratio)
ggplot(Movies, aes(x = Content_Rating, fill = Aspect_Ratio)) +
  geom_bar(position = "fill") +
  labs(title = "Content rating vs Aspect Ratio",
       x = "Content rating",
       y = "Proportion",
       fill = "Aspect Ratio")
# Result: Nothing meaningful to decipher

# Content rating vs Budget
## Calculate mean budget by content rating
mean_budget <- Movies %>% 
  group_by(Content_Rating) %>%
  summarise(mean_budget = mean(Budget, na.rm = TRUE))
## Plot
ggplot(mean_budget, aes(x = Content_Rating, y = mean_budget)) +
  geom_bar(stat = "identity", fill = "black", color = "black") +
  geom_text(aes(label = sprintf("%.1e", mean_budget)),
            position = position_stack(vjust = 0.5), color = "red") +
  labs(title = "Content rating vs Mean Budget",
       x = "Content Rating",
       y = "Mean Budget") +
  theme_classic()
# Result: Big difference in mean budget between G, PG, PG-13, R & NC-17, Not rated # TV-G, Unrated, NA.

# Content rating vs Reviews by users
## Calculate mean reviews by users earnings by content rating
mean_rbu <- Movies %>% 
  group_by(Content_Rating) %>%
  summarise(mean_rbu = mean(Reviews_by_Users, na.rm = TRUE))
## Plot
ggplot(mean_rbu, aes(x = Content_Rating, y = mean_rbu)) +
  geom_bar(stat = "identity", fill = "black", color = "black") +
  labs(title = "Content rating vs Mean Reviews by users",
       x = "Content Rating",
       y = "Mean Reviews by users") +
  theme_classic()
# Result: Nothing meaningful to decipher

# Content rating vs Reviews by critics
## Calculate mean reviews by critics earnings by content rating
mean_rbc <- Movies %>% 
  group_by(Content_Rating) %>%
  summarise(mean_rbc = mean(Reviews_by_Crtiics, na.rm = TRUE))
## Plot
ggplot(mean_rbc, aes(x = Content_Rating, y = mean_rbc)) +
  geom_bar(stat = "identity", fill = "black", color = "black") +
  labs(title = "Content rating vs Mean Reviews by critics",
       x = "Content Rating",
       y = "Mean Reviews by critics") +
  theme_classic()
# Result: Nothing meaningful to decipher

# Result for other variables: Too many levels to find anything meaningful
```

## Duration vs dependent variables

First the content rating and the target variable is compared, to determine whether a relationship/correlation exists between them. If there is no correlation/relationship between them, then it is to be excluded (in the cleaned data set), and therefore it is meaningless to compare the duration with other independent variables. However, I have done it just in case...

NOTE: We haven't yet decided which variable will be our target variable: IMDB score or Gross earnings, so both variables have been analysed

```{r}
# Duration vs IMDB score
ggplot(Movies, aes(x = Movies$Duration, y = Movies$IMDB_Score)) +
  geom_point()
# Result: Nothing meaningful to decipher i.e., no correlation

summary(lm(Movies$IMDB_Score~Movies$Duration))
# Result: They are statistically significant, but the r^2 value is very low (10%)
```

```{r}
# Duration vs Gross earnings
ggplot(Movies, aes(x = Movies$Duration, y = Movies$Gross_Earnings)) +
  geom_point()
# Result: Nothing meaningful to decipher i.e., no correlatione

summary(lm(Movies$Gross_Earnings~Movies$Duration))
# Result: They are statistically significant, but the r^2 value is very low (7.2%)
```

# Duration vs other independent variables

```{r}
# Duration vs Year
## Calculate mean duration by year
mean_duration_year <- Movies %>%
  group_by(Year) %>%
  summarise(mean_duration_year = mean(Duration, na.rm = TRUE))
## Plot
ggplot(mean_duration_year, aes(x = Year, y = mean_duration_year)) +
  geom_bar(stat = "identity", fill = "black", color = "black") +
  geom_text(aes(label = sprintf("%.1f", mean_duration_year)),
            position = position_stack(vjust = 0.5), color = "red") +
  labs(title = "Mean Duration vs Year",
       x = "Year",
       y = "Mean Duration") +
  theme_classic()
# Result: Mean duration was similar for all years in the dataset

# Duration vs Language
ggplot(Movies, aes(x = Movies$Language, y = Movies$Duration)) +
  geom_boxplot() +
  theme_classic()
# Result: Nothing meaningful to decipher

# Duration vs Country
ggplot(Movies, aes(x = Movies$Country, y = Movies$Duration)) +
  geom_boxplot() +
  theme_classic()
# Result: Nothing meaningful to decipher

# Duration vs Aspect ratio
ggplot(Movies, aes(x = Movies$Aspect_Ratio, y = Movies$Duration)) +
  geom_boxplot() +
  theme_classic()
# Result: The median duration of most aspect ratio types are similar

# Duration vs Budget
ggplot(Movies, aes(x = Movies$Aspect_Ratio, y = Movies$Budget)) +
  geom_boxplot() +
  theme_classic()

budget_range <- c(0, 1.25e+09)
filtered_movies <- subset(Movies, Budget >= budget_range[1] & Budget <= budget_range[2])

ggplot(filtered_movies, aes(x = Aspect_Ratio, y = Budget)) +
  geom_boxplot() +
  theme_classic()
# Result: 

# Result for other variables: Too many levels to find anything meaningful
```

# Aspect ratio vs dependent variables

First the content rating and the target variable is compared, to determine whether a relationship/correlation exists between them. If there is no correlation/relationship between them, then it is to be excluded (in the cleaned data set), and therefore it is meaningless to compare the aspect ratio with other independent variables.

NOTE: We haven't yet decided which variable will be our target variable: IMDB score or Gross earnings, so both variables have been analysed

```{r}
summary(aov(Movies$IMDB_Score~Movies$Aspect_Ratio, data=Movies))
```

```{r}
# Calculate the R - squared value
SvAR_model <- summary(lm(Movies$IMDB_Score ~ Movies$Aspect_Ratio, data = Movies))
# R-squared value from the summary
SvAR_model_R2 <- SvAR_model$r.squared
print(SvAR_model_R2)
# Result: They are statistically significant, but the r^2 value is extremely low (1.9%)
```

# Quick r\^2 value test of dependent variable vs other independent variables

## For target variable: Gross earnings

```{r}

# Gross_Earnings vs Year
summary(lm(Movies$Gross_Earnings~Movies$Year, data=Movies))
# Result: 0.2% r^2 value

# Gross_Earnings vs Language
GEvL_model <- summary(lm(Movies$Gross_Earnings~Movies$Language, data=Movies))
r_squared_Language <- GEvL_model$r.squared
print(r_squared_Language)
# Result: 2.5% r^2 value

# Gross_Earnings vs Country
GEvC_model <- summary(lm(Movies$Gross_Earnings~Movies$Country, data=Movies))
r_squared_Country <- GEvC_model$r.squared
print(r_squared_Country)
# Result: 4.8% r^2 value

# Gross_Earnings vs Budget
summary(lm(Movies$Gross_Earnings~Movies$Budget, data=Movies))
# Result: 0.35% r^2 value

# Gross_Earnings vs Reviews_by_Users
summary(lm(Movies$Gross_Earnings~Movies$Reviews_by_Users, data=Movies))
# Result: 39% r^2 value

# Gross_Earnings vs Reviews_by_Crtiics
summary(lm(Movies$Gross_Earnings~Movies$Reviews_by_Crtiics, data=Movies))
# Result: 27% r^2 value
```

## For target variable: IMDB score

```{r}
# IMDB score vs Year
summary(lm(Movies$IMDB_Score~Movies$Year, data=Movies))
# Result: 0.45% r^2 value

# IMDB score vs Language
GEvL_model <- summary(lm(Movies$IMDB_Score~Movies$Language, data=Movies))
r_squared_Language <- GEvL_model$r.squared
print(r_squared_Language)
# Result: 4.9% r^2 value

# IMDB score vs Country
GEvC_model <- summary(lm(Movies$IMDB_Score~Movies$Country, data=Movies))
r_squared_Country <- GEvC_model$r.squared
print(r_squared_Country)
# Result: 6.3% r^2 value

# IMDB score vs Budget
summary(lm(Movies$IMDB_Score~Movies$Budget, data=Movies))
# Result: 0.1% r^2 value

# IMDB score vs Reviews_by_Users
summary(lm(Movies$IMDB_Score~Movies$Reviews_by_Users, data=Movies))
# Result: 8.1% r^2 value

# IMDB score vs Reviews_by_Crtiics
summary(lm(Movies$IMDB_Score~Movies$Reviews_by_Crtiics, data=Movies))
# Result: 16.5% r^2 value
```
