---
title: "EDA-(Budget,Country)"
output: html_document
date: "2024-02-26"
---

```{r}
# loading all the required libraries with `library()`.  

library(tidyverse) 
library(ggplot2)   # Create customizable plots and charts with the Grammar of Graphics.
library(validate)  # Perform data validation and quality checks for enhanced data integrity.
library(Hmisc)     
```

# 1. Organise and clean the data

## 1.1 Import Dataset

```{r}
movies_df <- read.csv("movies_clean.csv",na.strings=c("","NA"))
```

# 2. EDA Analysis
```{r}
summary(movies_df)
```
```{r}

#Converting data type of all the genres into factor for ease in finding correlations.
movies_df$News <- factor(movies_df$News)
movies_df$Short <- factor(movies_df$Short)
movies_df$War <- factor(movies_df$War)
movies_df$Adventure<- factor(movies_df$Adventure)
movies_df$Animation <- factor(movies_df$Animation)
movies_df$Comedy <- factor(movies_df$Comedy)

movies_df$Family <- factor(movies_df$Family)
movies_df$Fantasy<- factor(movies_df$Fantasy)
movies_df$Sci_Fi <- factor(movies_df$Sci_Fi)
movies_df$Drama <- factor(movies_df$Drama)
movies_df$Romance <- factor(movies_df$Romance)
movies_df$Western <- factor(movies_df$Western)
movies_df$Crime <- factor(movies_df$Crime)
movies_df$Thriller <- factor(movies_df$Thriller)
movies_df$Action <- factor(movies_df$Action)
movies_df$Horror <- factor(movies_df$Horror)
movies_df$Music <- factor(movies_df$Music)
movies_df$Mystery <- factor(movies_df$Mystery)

```
```{r}
movies_df$Sport <- factor(movies_df$Sport )
movies_df$Musical <- factor(movies_df$Musical)
movies_df$Biography <- factor(movies_df$Biography)
movies_df$Documentary <- factor(movies_df$Documentary)
movies_df$History <- factor(movies_df$History)

```
```{r}

# columns to convert to numeric
columns_to_convert <- c("Duration", "Budget", "Aspect_Ratio", "Gross_Earnings", "Reviews_by_Users","Reviews_by_Crtiics")

# Convert specified columns to numeric
movies_df[columns_to_convert] <- lapply(movies_df[columns_to_convert], as.numeric)
```

## EDA for "Budget"
### 2.1. Univariate Analysis

```{r}
#For Budget
hist(movies_df$Budget,main="Distribution of Budget",xlab="Budget")
```
It is skewed to the left due to a huge number of missing values which affects the mean and median values. Hence, we can conclude Budget is not normally distributed. 

## 2.2. Bivariate Analysis
Budget variable with categorical variables
```{r}

#  a data frame with all the genres columns
genre_cols <- c("Adventure","Family","Romance","Western","Music","Crime","Mystery","Sport","Animation","Musical","Biography","Documentary","History","War","Short","News","Comedy", "Action", "Drama", "Horror", "Sci_Fi", "Fantasy", "Thriller") 

genre_budget_df <- movies_df[, c("Budget", genre_cols)]

# Convert binary indicators to factor variables
genre_budget_df[genre_columns] <- lapply(genre_budget_df[genre_columns], factor)

# Reshape the data from wide to long format for visualization
genre_budget_long <- tidyr::gather(genre_budget_df, key = "Genre", value = "Indicator", -Budget)

# Plot showing mean budget for different genres
ggplot(genre_budget_long, aes(x = Genre, y = Budget, fill = Indicator)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Mean Budget for Different Genres",
       x = "Genre",
       y = "Mean Budget") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = c("lightblue", "pink")) # Adjust colors as needed

# Bar plot showing mean budget for different languages
movies_df %>%
  group_by(Language) %>%
  summarise(mean_budget = mean(Budget, na.rm = TRUE)) %>%
  ggplot(aes(x = Language, y = mean_budget)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Mean Budget for Different Languages")

# Bar plot showing mean budget for different countries
movies_df %>%
  group_by(Country) %>%
  summarise(mean_budget = mean(Budget, na.rm = TRUE)) %>%
  ggplot(aes(x = Country, y = mean_budget)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Mean Budget for Different Countries")

# Bar plot showing mean budget for different content ratings
ggplot(movies_df, aes(x = Content_Rating, y = Budget)) +
  stat_summary(fun = mean, geom = "bar") +
  labs(title = "Mean Budget by Content Rating",
       x = "Content Rating",
       y = "Mean Budget")

```

-The above graphs indicate that the distribution among our dependent variable "Budget" and independent categorical variables is not normal and also give us an overview of how the budget is distributed across each variable. 


-As Budget does not follows a normal distribution we will use Kruskal-Wallis Test for identifying its correlation with the categorical variables
```{r}
# Budget vs Content_Rating
kruskal_result <- kruskal.test(Budget ~ Content_Rating,data=movies_df)

# Print the Kruskal-Wallis test result
print(kruskal_result)
```
As the p-value is < 0.05 we can conclude that there is a significant relation between Budget and Content_Rating.

```{r}
# # Budget vs Genres
kruskal_result <- kruskal.test(Budget ~ Genres,data=movies_df)

# Print the Kruskal-Wallis test result
print(kruskal_result)
```
As the p-value is < 0.05 we can conclude that there is a significant relation between Budget and Genres.
```{r}
# Budget vs Language
kruskal_result <- kruskal.test(Budget ~ Language,data=movies_df)

# Print the Kruskal-Wallis test result
print(kruskal_result)
```
As the p-value is < 0.05 we can conclude that there is a significant relation between Budget and Language.
```{r}
# # Budget vs Country
kruskal_result <- kruskal.test(Budget ~ Country,data=movies_df)

# Print the Kruskal-Wallis test result
print(kruskal_result)
```
As the p-value is < 0.05 we can conclude that there is a significant relation between Budget and Country.
```{r}
# Budget vs Director
 kruskal_test <- kruskal.test(Budget ~ Director, movies_df)
  print(kruskal_test)
```
As the p-value is < 0.05 we can conclude that there is a significant relation between Budget and Director. 

```{r}

# # Budget vs Actors
kruskal_resultA1 <- kruskal.test(Budget ~ Actor1,data=movies_df)
kruskal_resultA2 <- kruskal.test(Budget ~ Actor2,data=movies_df)
kruskal_resultA3 <- kruskal.test(Budget ~ Actor3,data=movies_df)


# Print the Kruskal-Wallis test result
print(kruskal_resultA1)
print(kruskal_resultA2)
print(kruskal_resultA3)

```
For Actor 1, As the p-value is < 0.05 we can conclude that there is a significant relation between Budget and Actor 1.
For Actor2, As the p-value is < 0.05 we can conclude that there is a significant relation between Budget and Actor 2.
Actor3, Although the p-value is <0.05 we can conclude that there is a significant relation between Budget and Actor3.

## 2.3. Multivariate Analysis


```{r}
# Select only numeric variables and neglect NA values
numeric_data <- movies_df %>%
  select_if(~ is.numeric(.))

# Calculate correlation matrix while neglecting NA values
correlation_matrix <- cor(numeric_data, use = "pairwise.complete.obs")

# View correlation matrix
print(correlation_matrix)
```
## EDA for "Country" Variable
```{r}
#For Country

# Count the number of movies produced in each country
country_counts <- table(movies_df$Country)

# Convert the table to a data frame
country_counts_df <- as.data.frame(country_counts)

# Sort the data frame by movie counts in descending order
country_counts_df <- country_counts_df[order(-country_counts_df$Freq), ]

# Plot
barplot(country_counts_df$Freq, 
        names.arg = country_counts_df$Var1, 
        main = "Number of Movies Produced by Country",
        xlab = "Country", ylab = "Number of Movies",
        col = "skyblue",
        las = 2, # Rotate x-axis labels vertically for better readability
        cex.names = 0.7) # Adjust size of x-axis labels

```
This plot shows that most of the data we have is from USA. 

```{r}
#Country vs Year
chi_squared_result <- chisq.test(movies_df$Country, movies_df$Year)
print(chi_squared_result)

#Country vs Duration
chi_squared_result <- chisq.test(movies_df$Country, movies_df$Duration)
print(chi_squared_result)

#Country vs Aspect_Ratio
chi_squared_result <- chisq.test(movies_df$Country, movies_df$Aspect_Ratio)
print(chi_squared_result)

#Country vs Budget
chi_squared_result <- chisq.test(movies_df$Country, movies_df$Budget)
print(chi_squared_result)

#Country vs Gross_Earnings
chi_squared_result <- chisq.test(movies_df$Country, movies_df$Gross_Earnings)
print(chi_squared_result)

#Country vs Reviews_by_Users
chi_squared_result <- chisq.test(movies_df$Country, movies_df$Reviews_by_Users)
print(chi_squared_result)

#Country vs Reviews_by_Crtiics
chi_squared_result <- chisq.test(movies_df$Country, movies_df$Reviews_by_Crtiics)
print(chi_squared_result)

#Country vs IMDB_Score
chi_squared_result <- chisq.test(movies_df$Country, movies_df$IMDB_Score)
print(chi_squared_result)

```
The test results of our dependent variable "Country" with other independent numeric variables represent that its dependent on "Duration","Budget" and "IMDB_SCORE". 

```{r}
#Country vs Genres
chi2_result <- chisq.test(table(movies_df$Country, movies_df$Genres))
print(chi2_result)

#Country vs Language
chi2_result <- chisq.test(table(movies_df$Country,movies_df$Language))
print(chi2_result)

#Country vs Director
chi2_result <- chisq.test(table(movies_df$Country,movies_df$Director))
print(chi2_result)

#Country vs Content_Rating
chi2_result <- chisq.test(table(movies_df$Country,movies_df$Content_Rating))
print(chi2_result)

#Country vs Actor1
chi2_result <- chisq.test(table(movies_df$Country,movies_df$Actor1))
print(chi2_result)

#Country vs Actor2
chi2_result <- chisq.test(table(movies_df$Country,movies_df$Actor2))
print(chi2_result)

#Country vs Actor3
chi2_result <- chisq.test(table(movies_df$Country,movies_df$Actor3))
print(chi2_result)

```
Our test results for our dependent variable "Country" shows that it depends on Genres, director, language, Actor1 and Actor2. The test results for Content_Rating and Actor3 are shows p-value that is NA which is due to missing values for one or more category.


